Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
move on arch
fix placement
simplify a bit

@@

\begin{figure}[bh]
\begin{center}
\includegraphics{architecture.pdf}
\caption{Architectural overview. The proposed system is represented
  inside the box titled ``Proxy''. It interacts with a client, a
  Triple Patterns Fragments Server and a SPARQL Endpoint. The most
  important component is the query engine, which consists of a query
  planner and a query evaluator.}\label{fig:arch}
\end{center}
\end{figure}

@@

@@

When a query is parsed, algebra objects are generated. Based on the
algebra tree, models may generate plans for any algebra object of
their choosing by implementing the \pmodule{Attean::API::CostPlanner}
role. This amounts to implementing \pcode{plans\_for\_algebra} and
\pcode{cost\_for\_plan} methods. For a given algebra, Attean's query
planner will trust that the model's \pcode{plans\_for\_algebra} is
better than its own by default, a choice that was justified in
\cite{williamspushing}. Additionally, Attean has a simpler mechanism
for single quad patterns: By default, quad patterns are evaluated by
calling the Model's \pcode{get\_quads}, but this may be augmented by
adding a wrapper around an \pcode{access\_plans} method used by the
query planner to produce further plans.

@@

The caching proxy consists of several components:

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics{architecture.pdf}
\caption{Architectural overview. The proposed system is represented
  inside the box titled ``Proxy''. It interacts with a client, a
  Triple Patterns Fragments Server and a SPARQL Endpoint. The most
  important component is the query engine, which consists of a query
  planner and a query evaluator.}\label{fig:arch}
\end{center}
\end{figure}

@@

@@

This section explores the implementation of the general architecture
outlined in Section~\ref{sec:arch}.

@@

Based on the algebra tree from a parsed query (see
Section~\ref{sec:understandquery} for details), models may generate
plans for any algebra object of
their choosing by implementing the \pmodule{Attean::API::CostPlanner}
role. This amounts to implementing \pcode{plans\_for\_algebra} and
\pcode{cost\_for\_plan} methods. For a given algebra, Attean's query
planner will trust that the model's \pcode{plans\_for\_algebra} is
better than its own by default, a choice that was justified in
\cite{williamspushing}. Additionally, Attean has a simpler mechanism
for single quad patterns: By default, quad patterns are evaluated by
calling the Model's \pcode{get\_quads}, but this may be augmented by
adding a wrapper around an \pcode{access\_plans} method used by the
query planner to produce further plans.

@@

The caching proxy consists of several components, detailing the
overview in Figure~\ref{fig:arch}:
